% list of conferences

\nocite{*}
\bibliographystyle{cv}
%\bibliography{conferences}
\begin{thebibliography}{10}
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{Reis and Oliveira~Jr.(2017)}]{latinmag_2017}
Reis, A. L.~A. and Oliveira~Jr., V.~C.
\newblock Sed for optimal acquisition design and sensor-to-sample distance
  applied to scanning magnetic microscopy.
\newblock In \emph{Fifth bi-anual meeting of the LATINMAG}. LATINMAG,
  Quer\'{e}taro, M\'{e}xico, 2017.
\newblock Participation type: Abstract co-author.

\bibitem[{Hallam and Oliveira~Jr.(2016)}]{agu_fallmeeting_2016b}
Hallam, K. A.~T. and Oliveira~Jr., V.~C.
\newblock Applications of differential operators in geodetic coordinates.
\newblock In \emph{2016 AGU Fall Meeting}. AGU, San Francisco, USA, 2016.
\newblock Participation type: Abstract co-author.

\bibitem[{Reis and Oliveira~Jr.(2016)}]{agu_fallmeeting_2016a}
Reis, A. L.~A. and Oliveira~Jr., V.~C.
\newblock Impact of the sensor area, acquisition design and position noise on
  the estimation of the magnetization distribution within a rectangular rock
  sample.
\newblock In \emph{2016 AGU Fall Meeting}. AGU, San Francisco, USA, 2016.
\newblock Participation type: Abstract co-author.

\bibitem[{Oliveira~Jr. et~al.(2015)Oliveira~Jr., Sales, Barbosa, and
  Uieda}]{iugg_2015a}
Oliveira~Jr., V.~C., Sales, D.~P., Barbosa, V. C.~F., and Uieda, L.
\newblock Estimating the total magnetization direction of approximately
  spherical bodies.
\newblock In \emph{26th IUGG General Assembly - IAGA - A41 Lithospheric Field
  Modeling, the WDMAM and Tectonic Implications (Div. V) - A41p-280}. IUGG,
  Prague, Czech Republic, 2015.
\newblock Participation type: Abstract co-author, Poster presentation.

\bibitem[{Reis et~al.(2015)Reis, Oliveira~Jr., Yokoyama, Bruno, and
  Pereira}]{iugg_2015b}
Reis, A. L.~A., Oliveira~Jr., V.~C., Yokoyama, E., Bruno, A.~C., and Pereira,
  J. M.~B.
\newblock Estimating the magnetization distribution within rectangular rock
  samples.
\newblock In \emph{26th IUGG General Assembly - IAGA - A06d-A06d A06/A07
  Applied Rock Magnetism (Div. I) / Theoretical and Experimental Rock Magnetism
  (Div. I) - IUGG-1853}. IUGG, Prague, Czech Republic, 2015.
\newblock Participation type: Abstract co-author, Oral presentation.

\bibitem[{Oliveira~Jr. and Barbosa(2014)}]{eage_2014}
Oliveira~Jr., V.~C. and Barbosa, V. C.~F.
\newblock 3-d radial gravity gradient inversion applied to the interpretation
  of the vinton salt dome, usa.
\newblock In \emph{76th EAGE Conference and Exhibition 2014}. EAGE, Amsterdam,
  Netherlands, 2014.
\newblock Participation type: Expanded abstract author, Oral presentation.

\bibitem[{Uieda et~al.(2013)Uieda, Oliveira~Jr., and Barbosa}]{scipy_2013}
Uieda, L., Oliveira~Jr., V.~C., and Barbosa, V. C.~F.
\newblock Modeling the earth with fatiando a terra.
\newblock In \emph{12th Scientific Computing with Python Conference}. SciPy,
  Austin, USA, 2013.
\newblock Participation type: Expanded abstract co-author.

\bibitem[{Oliveira~Jr. and Barbosa(2012)}]{seg_2012}
Oliveira~Jr., V.~C. and Barbosa, V. C.~F.
\newblock Polynomial equivalent layer.
\newblock In \emph{SEG Las Vegas 2012 Annual Meeting}. SEG, Las Vegas, USA,
  2012.
\newblock Participation type: Expanded abstract author.

\bibitem[{Oliveira~Jr. and Barbosa(2011{\natexlab{a}})}]{eage_2011}
Oliveira~Jr., V.~C. and Barbosa, V. C.~F.
\newblock 3d radial inversion of gravity data for estimating the source's
  geometry.
\newblock In \emph{73rd EAGE Conference and Exhibition incorporating SPE EUROPEC
  2011}. EAGE, Vienna, Austria, 2011{\natexlab{a}}.
\newblock Participation type: Expanded abstract author, Oral presentation.

\bibitem[{Oliveira~Jr. and Barbosa(2011{\natexlab{b}})}]{seg_2011}
Oliveira~Jr., V.~C. and Barbosa, V. C.~F.
\newblock Radial gravity inversion constrained by total anomalous mass excess
  for retrieving 3d bodies.
\newblock In \emph{SEG San Antonio 2011 Annual Meeting}. SEG, San Antonio, USA,
  2011{\natexlab{b}}.
\newblock Participation type: Expanded abstract author.

\end{thebibliography}
